Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases

### 2021-07-14 submission/submission.tex

Compared to other approaches, this use can provide several
improvements:
\begin{itemize}
\item The user does not disclose his passphrase. Most other approaches
  (based on hashes for example) give an opportunity for
  man-in-the-middle attacks;
\item As the user does not disclose his passphrase, the pubkey can be
  replaced several times;
\item The user does not need to create the new public key ahead of
  time. Instead, he can create it when he has lost the former one,
  decreasing the likelihood of losing the associated secret key also;
\end{itemize}

@@

This use case includes 3 different components:
\begin{description}
\item[PinCode Client:] it is a C++ program linked to the Blueprint
  \zksnarks{} library. It can be used in two different ways:
  \begin{itemize}
  \item To create the initial circuit using the passphrase. The client
    should be called as:
\begin{verbatim}
pincode-client prepare "my pass phrase"
\end{verbatim}
   This will generate a file \lstinline{verifkey.hex} that can be used
   as an argument when deploying the \lstinline{PubkeyRecovery} smart
   contract, and a file \lstinline{provkey.hex} that can be used to
   create new witnesses;
 \item To create a witness that the passphrase is known when providing
   a new public key. Because the witness contains the new public key,
   an attacker cannot intercept the message and replace it. The client
   should be called as:
\begin{verbatim}
pincode-client prove "my pass phrase" "PUBKEY_AS_HEX_NUMBER"
\end{verbatim}
  The command expects to find the file \lstinline{provkey.hex} and
  generates a file \lstinline{proof.hex} that should be submitted to
  the \lstinline{PubkeyRecovery} smart contract together with the new
  public key.
  \end{itemize}
\item[PubkeyRecovery smart contract:] This smart contract is a
  contract à la TIP-3 contract, using the initial public key to verify
  its address. This contract is very simple. It contains:
  \begin{itemize}
  \item A constructor to set the circuit that will be used to verify
    that the passphrase is known when it is used;
  \item An external function
    \lstinline{SetFromPincode(bytes proof, uint256 pubkey)}
    to define the new public key, while providing a
    proof of knowledge of the passphrase;
  \item An external function
    \lstinline{RecoverPubkey(RecoverablePubkey addr)} to call a
    recoverable contract to update the corresponding pubkey.
  \end{itemize}
\item[Abstract RecoverablePubkey contract:] This is an abstract
  contract, from which other contracts should inherit to be able to
  benefit from the {\tt PubkeyRecovery} mechanism. The contract
  provides two main functions:
  \begin{itemize}
  \item An external function \lstinline{SetPubkeyRecoveryCode(TvmCell
    code)} to define the code of the \lstinline{PubkeyRecovery} smart
    contract. Because the code hash is known (inlined in the code),
    anybody can call this function with the correct code.
  \item An external function \lstinline{RecoverPubkey(uint256 oldkey,
    uint256 newkey)} that can only be called by a
    \lstinline{PubkeyRecovery} smart contract. The function verifies
    that the address belongs to such a contract before calling a
    function \lstinline{recover\_pubkey(oldkey, newkey)}, that the
    inheriting contract should define to specify the business logic
    that should happen when a pubkey is replaced.
  \end{itemize}
\item[Modified Multisig Wallet:] The
  \lstinline{RecoverableMultisigWallet} contract is the standard
  multisig wallet of Surf, updated for version 0.40 of Solidity, and
  modified to inherit from the \lstinline{RecoverablePubkey}
  contract. It defines the business logic to replace a custodian key.
  For that, it first checks that the old key belongs to an existing
  custodian of the contract, that the new key does not belong to an
  existing custodian, and then replace the old key by the new one,
  associated to the same index (for bitfields).
\end{description}

>>>>

Compared to other approaches, this use can provide several
improvements:
\begin{itemize}
\item The user does not disclose his passphrase. Most other approaches
  (based on hashes for example) give an opportunity for
  man-in-the-middle attacks;
\item As the user does not disclose his passphrase, the pubkey can be
  replaced several times;
\item The user does not need to create the new public key ahead of
  time. Instead, he can create it when he has lost the former one,

  decreasing the likelihood of losing the associated secret key also.
\end{itemize}

@@

This use case includes 3 different components:
\begin{description}
\item[PinCode Client:] it is a C++ program linked to the Blueprint
  \zksnarks{} library. It can be used in two different ways:
  \begin{itemize}
  \item To create the initial circuit using the passphrase. The client
    should be called as:
\begin{verbatim}
pincode-client prepare "my pass phrase"
\end{verbatim}
   This will generate a file \lstinline{verifkey.hex} that can be used
   as an argument when deploying the \lstinline{PubkeyRecovery} smart
   contract, and a file \lstinline{provkey.hex} that can be used to
   create new witnesses;
 \item To create a witness that the passphrase is known when providing
   a new public key. Because the witness contains the new public key,
   an attacker cannot intercept the message and replace it. The client
   should be called as:
\begin{verbatim}
pincode-client prove "my pass phrase" "PUBKEY_AS_HEX_NUMBER"
\end{verbatim}
  The command expects to find the file \lstinline{provkey.hex} and
  generates a file \lstinline{proof.hex} that should be submitted to
  the \lstinline{PubkeyRecovery} smart contract together with the new
  public key.
  \end{itemize}
\item[PubkeyRecovery smart contract:] This smart contract is a
  contract à la TIP-3 contract, using the initial public key to verify
  its address. This contract is very simple. It contains:
  \begin{itemize}
  \item A constructor to set the circuit that will be used to verify
    that the passphrase is known when it is used;
  \item An external function
    \lstinline{SetFromPincode(bytes proof, uint256 pubkey)}
    to define the new public key, while providing a
    proof of knowledge of the passphrase;
  \item An external function
    \lstinline{RecoverPubkey(RecoverablePubkey addr)} to call a
    recoverable contract to update the corresponding pubkey.
  \end{itemize}
\item[Abstract RecoverablePubkey contract:] This is an abstract
  contract, from which other contracts should inherit to be able to
  benefit from the {\tt PubkeyRecovery} mechanism. The contract
  provides two main functions:
  \begin{itemize}
  \item An external function \lstinline{SetPubkeyRecoveryCode(TvmCellcode)} to define the code of the \lstinline{PubkeyRecovery} smart
    contract. Because the code hash is known (inlined in the code),
    anybody can call this function with the correct code.
  \item An external function \lstinline{RecoverPubkey(uint256 oldkey,uint256 newkey)} that can only be called by a
    \lstinline{PubkeyRecovery} smart contract. The function verifies
    that the address belongs to such a contract before calling a
    function \lstinline{recover\_pubkey(oldkey, newkey)}, that the
    inheriting contract should define to specify the business logic
    that should happen when a pubkey is replaced.
  \end{itemize}
\item[Modified Multisig Wallet:] The
  \lstinline{RecoverableMultisigWallet} contract is the standard
  multisig wallet of Surf, updated for version 0.40 of Solidity, and
  modified to inherit from the \lstinline{RecoverablePubkey}
  contract. It defines the business logic to replace a custodian key.
  For that, it first checks that the old key belongs to an existing
  custodian of the contract, that the new key does not belong to an
  existing custodian, and then replace the old key by the new one,
  associated to the same index (for bitfields).
\end{description}
